---
subtitle: "Project Proposal"
author: "Pipe It Up!: Nagaprasad Rudrapatna, Karen Deng, Jack Muraika, Anna Zolotor"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r load-packages}
library(tidyverse)
library(broom)
library(stringr)
library(knitr)
```

```{r load-data}
nba_social_power <- read_csv("data/nba_2016_2017_100.csv")
```

**ERASE ALL INSTRUCTIONS BEFORE SUBMITTING THE PROPOSAL**

### Project Description


- What is the research question you wish to explore? 
*This includes an introduction to the subject matter you’re investigating, the motivation for the for your research question (citing any relevant literature), and your hypotheses regarding the research question of interest.*


- Describe the dataset you wish to explore. 
*This includes describing the observations in the data, a general description of the variables, and how the data was originally collected (not how you found the data but how the original curator of the data collected it.)*

## The Data

Finally, we will examine the relevant variables in the dataset:

```{r glimpse-nba-social-power}
glimpse(nba_social_power) # entire dataset

nba_social_power_mod <- nba_social_power %>%
  filter(TWITTER_HANDLE != "0") %>%
  select(PLAYER_NAME, 
         TEAM_ABBREVIATION,
         AGE,
         W_PCT,
         OFF_RATING,
         DEF_RATING,
         NET_RATING,
         AST_RATIO,
         REB_PCT,
         USG_PCT,
         PIE,
         SALARY_MILLIONS,
         ACTIVE_TWITTER_LAST_YEAR,
         TWITTER_FOLLOWER_COUNT_MILLIONS,
         PTS) 

glimpse(nba_social_power_mod) # modified dataset for analysis
```

